### 2021-06-23 src/paper/appendix_results.tex
Add figures on rapid test shares in the results appendix.

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_doing_rapid_test_today}
  \caption{Share of Individuals Doing a Rapid Test per Day}
  \label{fig:fit_share_doing_rapid_test}
  \floatfoot{\noindent \textit{Note:} The plateau in the end is the result of falling
  case numbers that lead to less private rapid tests being demanded due to contact
  tracing. The two biggest jumps are due to public holidays, i.e. the end of Easter
  vacations in the first half of April and May 1st. These lead many individuals to not
  test themselves (even though the threshold to be tested falls during the time) due to
  vacations from school and work. As a result more individuals than usual are due to be
  tested because of frequency requirements after public holidays. }
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
  \caption{Share of Individuals That has Ever Done a Rapid Test}
  \label{fig:fit_share_ever_rapid_test}
  \floatfoot{\noindent \textit{Note:} This figure clearly shows that overall our
  assumptions on rapid tests are conservative. In our model, the share of individuals who
  have ever done a rapid test lies  consistently 10 percentage points below the share
  reported in the COSMO study \citep{Betsch2021}. The main reason for this is that we
  introduce rapid tests only at the start of 2021. However, using the available data to
  calibrate our rapid test parameters and estimating the remaining parameters to fit the
  official case numbers we arrive at a shape that is very similar to that implied by the
  survey results. This together with fitting the share of Germans with weekly rapid tests
  well (see Figure~\ref{fig:fit_share_rapid_test_within_last_week} makes us confident
  that our rapid test model is a good -- and especially not over-confident --
  representation of rapid testing in Germany.}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
  \caption{Share of Individuals Who Have Done a Rapid Test in the Last Week}
  \label{fig:fit_share_rapid_test_within_last_week}
  \floatfoot{\noindent \textit{Note:} The two lines are not perfectly compatible. The
  COSMO study \citep{Betsch2021} only asked if individuals had done at least one
  self-administered rapid test per week in the last four weeks. This means there are two
  differences between the simulated line and the empirical data points. Firstly, the
  simulated line encompasses all rapid tests since we do not differentiate between
  self-administered and medically administered rapid tests. Secondly, in our model we
  cannot verify the rhythm over the last four weeks but just observe the last time of a
  rapid test. However, both work and school rapid tests which make up the largest share
  of rapid tests (see Figure~\ref{fig:rapid_test_demand_by_reason}) are both required on
  a weekly or twice weekly basis while the private rapid test demand which are partly
  just triggered by events make up only a small fraction of tests. }
\end{figure}
